TBD

### 2021-02-17 outputs/paper/paper.Rmd
Altered some graphs to stacked bars, 11th graph added
5, 6, and 13 remain to be done. 8 and 9 should probably be converted to line graphs to best display revenue changes between treatment and control groups

ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = position_dodge(1)) + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = "Q8",
       fill = "Type") +
  theme_minimal()

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = position_dodge(1)) +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "25% or less", "25-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = "Q9",
       fill = "Legend") +
  theme_minimal()

@@

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q15, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "How many days per week did you reduce by?",
       y = "# of restaurants",
       title = "Q15",
       fill = "Legend") +
  theme_minimal()

>>>>

ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = "Q8",
       fill = "Type") +
  theme_minimal()

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = "stack") +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "15% or less", "15-30%","30-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = "Q9",
       fill = "Legend") +
  theme_minimal()

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q11, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("UberEats", "SkiptheDishes", "DoorDash", "Other", "In-house delivery service", "None")) +
  labs(x = "Delivery Service",
       y = "# of Restaurants",
       title = "Q11",
       fill = "Legend") +
  theme_minimal()

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q15, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "How many days per week did you reduce by?",
       y = "# of restaurants",
       title = "Q15",
       fill = "Legend") +
  theme_minimal()
